Music Perception: Stimuli profiles

### 2021-05-31 material/expstimuli/selection/stimuli.Rmd
correct comments
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>
count the number of original performances
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

# Filtering
```{r filtering, eval = FALSE, include = FALSE}
# read functions
source("./function.R")

@@

# exclude IOIs +/- 3SD
dt_ioi <- dt_include[Key_OnOff == 1]
dt_ioi$IOI <- diff(c(0, dt_ioi$TimeStamp))
dt_ioi <- dt_ioi[NoteNr != 17] # remove irrelevant notes
dt_ioi$Interval <- rep(1:66, nrow(dt_ioi)/66)
ioi <- dt_ioi[Interval != 32 & Interval != 33 & Interval != 65 & Interval != 66, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, BlockNr, TrialNr)]
mean_ioi <- mean(ioi$Mean)
sd_ioi <- sd(ioi$Mean)
ioi_include <- ioi[Mean < mean_ioi+2*sd_ioi & Mean > mean_ioi-2*sd_ioi]

@@

## Histogram
- Gray vertical lines indicate ideal tempi (300ms for 100bpm, 273ms for 110bpm, 250ms for 120bpm)

1. Before exclusion
```{r plot-hist, echo = FALSE}
gghistogram(ioi, x = "Mean", rug = TRUE, add_density = TRUE, bins = 50) + geom_vline(xintercept = 188, color = "gray", size = 1)
```

2. After exclusion
```{r plot-hist2, echo = FALSE}
gghistogram(ioi_include, x = "Mean", rug = TRUE, add_density = TRUE, bins = 50) + geom_vline(xintercept = 188, color = "gray", size = 1)
```

@@

```{r stimuli, include = FALSE}
rm(list = ls()) # clear all

>>>>

# Filtering
```{r filtering, include = FALSE}
# read functions
source("./function.R")

@@

# exclude IOIs +/- 3SD
dt_ioi <- dt_include[Key_OnOff == 1]
dt_ioi$IOI <- diff(c(0, dt_ioi$TimeStamp))
dt_ioi <- dt_ioi[NoteNr != 17] # remove irrelevant notes
dt_ioi$Interval <- rep(1:66, nrow(dt_ioi)/66)
ioi_original <- dt_ioi[Interval != 32 & Interval != 33 & Interval != 65 & Interval != 66, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, BlockNr, TrialNr, Condition)]
mean_ioi <- mean(ioi_original$Mean)
sd_ioi <- sd(ioi_original$Mean)
ioi_include <- ioi_original[Mean < mean_ioi+2*sd_ioi & Mean > mean_ioi-2*sd_ioi]

@@

## IOIs Histogram
- Gray vertical lines indicate the ideal tempo (188ms for 80 bpm).

1. Before exclusion
```{r plot-hist, echo = FALSE}
gghistogram(ioi_original, x = "Mean", rug = TRUE, add_density = TRUE, bins = 50) + geom_vline(xintercept = 188, color = "gray", size = 1)
```
- the number of performances in the teaching condition: `r nrow(ioi_original[Condition == "teaching"])`
- the number of performances in the performing condition: `r nrow(ioi_original[Condition == "performing"])`

2. After exclusion
```{r plot-hist2, echo = FALSE}
gghistogram(ioi_include, x = "Mean", rug = TRUE, add_density = TRUE, bins = 50) + geom_vline(xintercept = 188, color = "gray", size = 1)
```
- the number of performances in the teaching condition: `r nrow(ioi_include[Condition == "teaching"])`
- the number of performances in the performing condition: `r nrow(ioi_include[Condition == "performing"])`

@@

```{r stimuli, include = FALSE}
#rm(list = ls()) # clear all
